---
title: "README"
author: "Moritz Lindner"
date: "20 January 2021"
output: github_document
---

## Installation
```{r Install, eval=FALSE, include=T}
remotes::install_github("moritzlindner/PatchMasteR")
```

## Description

Core component of PatchMasteR is the PMTrace class, wich stores a series imported from a Patchmaster *.dat file. Several integrety checks are implemented into the PMTrace class to assure data integrity is maintained.

## Examples

### Example 1:
Import a PatchMaster *.dat file, inspect visually and make an average over all sweeps 


```{r Example1, eval=FALSE, include=T}
library(PatchMasteR)

# import a PatchMaster file
tmp<-ImportPMSeries("test.dat",series = 1,traces = c(1,2))

# build a Plot superimposing all sweeps and inspect interactivley
tmp<-BuildSeriesPlot(tmp)
tmp<-InspectSeries(tmp, Trace = "I.mon")

# apply any function to the PMSeries object, in this case, make mean over all sweeps
tmp<-apply(tmp, "Sweep", mean, ReturnPMTRace = T)

# and return as data.frame
as.data.frame(tmp)
```

### Example 2:
Create a PMExperiment, perform a classical time series data extraction (in this case: from each stored PMSeries, take current trace "I-mon", extract values between 1s and 1.19s from sweep 15 and average these), and add thesse as metadata.
```{r Example2, eval=FALSE, include=T}

exp<-newPMExperiment(list(tmp,tmp),Names=c("A","B"),Group=c("Generic1","Generic2"))

AddMetaData(exp, #add as metadata to PMExperiment
            lapply(exp, # for each PMSeries stored in PMExperiment
                   function(x){
                     apply( # average over time
                       SubsetData(x, # extract values from I-mon trace, Sweep 15, between 1 and 1.19 s only 
                                  Traces="I-mon",
                                  Time =c(1,1.19)
                                  Sweeps=getSweeps(x)[c(15)]),
                       "Time",
                       mean)
                     }
                   )
            )

exp@MetaData

```

*The import functions have been adopted from the [ephys2 package](https://github.com/tdanker/ephys2) from Timm Danker*

Developed by [Moritz Lindner](https://www.uni-marburg.de/en/fb20/departments/physiology/research/dominik-oliver-lab/research2/retinal-physiology-and-gene-therapy)
